---
title: "Bordeau mixture analysis"
output:
  rmdformats::robobook:
    highlight: kate
editor_options: 
  chunk_output_type: inline
---

<style type="text/css">
.main-container {
  max-width: 1800px;
  margin-left: auto;
  margin-right: auto;
}
  body{
  font-size: 10pt;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F)
```

```{r include=FALSE}
pacman::p_load(tidyverse, janitor, metafor)
load("data/data.RData")
```

## Only Bordeaux mixture against non-treated check (overall)

### Control efficacy

```{r}
mv_inc_BM <- rma.mv(log_inc, vi,
                     mods = ~treatment,
                     random = list(~treatment | trial),
                     struct = "HCS",
                     method = "ML",
                     data = dat_bord)
mv_inc_BM
```


```{r}
efficacy_BM <- data.frame(cbind(
  (1 - exp(mv_inc_BM$b)) * 100,
  (1 - exp(mv_inc_BM$ci.ub)) * 100),
  (1 - exp(mv_inc_BM$ci.lb)) * 100
  )  %>% 
  set_names("control", "control_inf", "control_sup") %>% 
  rownames_to_column("treatment") %>% 
  mutate(treatment = str_replace(treatment, "treatment", "")) %>% 
  filter(treatment != "intrcpt") 

efficacy_BM
```

### Yield response 

```{r}
mv_yield_BM <- rma.mv(log_yield, log_var_yield,
                      mods = ~treatment,
                      random = list(~treatment | trial),
                      method = "ML",
                      struct = "HCS",
                      data = dat_bord)
mv_yield_BM
```

```{r}
yield_BM <- data.frame(cbind((exp(mv_yield_BM$b)-1)*100, 
                             (exp(mv_yield_BM$ci.lb)-1)*100,
                             (exp(mv_yield_BM$ci.ub)-1)*100)) %>%  
  set_names("yield_resp", "yield_resp.inf", "yield_resp.sup") %>% 
  rownames_to_column("treatment") %>% 
  mutate(treatment = str_replace(treatment, "treatment", "")) %>% 
  filter(treatment != "intrcpt")

yield_BM 
```

Table overall effect of BM in control efficacy and yield response

```{r}
inc_yield_BM <- inner_join(dat_bord %>% count(treatment),
                           full_join(efficacy_BM, yield_BM)) %>%
  mutate_if(is.numeric, round, 2)

inc_yield_BM %>%   
  knitr::kable()
```

## Disease pressure as moderator variable

```{r}
dat_bord %>% 
  ggplot()+
  aes(x=treatment, y =yield)+
  geom_point()+
  geom_line(aes(group=trial))+
  facet_wrap("inc_check_class")+
  theme_bw()

dat_bord %>% 
  group_by(treatment, inc_check_class) %>% 
  summarise(y=mean(yield))

```

### Yield response 

```{r}
mv_yield_BM_dispress <- rma.mv(log_yield, log_var_yield,
                      mods = ~treatment * inc_check_class,
                      random = list(~treatment | trial),
                      method = "ML",
                      struct = "UN",
                      data = dat_bord)
summary(mv_yield_BM_dispress)
```

```{r}
anova(mv_yield_BM_dispress, btt=3:4)
```

```{r}
dat_bord %>% 
  group_by(inc_check_class, treatment) %>% 
  summarise(y=mean(yield))
```

```{r}
net_D_dl <- rma.mv(yield, var_yield,
                   mods = ~treatment * inc_check_class,
                   random = list(~treatment | trial),
                   method = "ML",
                   struct = "UN",
                   # struct = "UN",
                   # control = list(optimizer = "nlm"),
                   data = dat_bord)
```

```{r}
res_D_dl <-
  with(net_D_dl,
       data.frame(
         Dis_level = rep(c("Low_DP", "High_DP"), e=1),
         fungi = gsub("fungic","", row.names(net_D_dl$b)[2]),
         D = round(c(b[2], b[2] + b[4]),1),
         SE = round(c(se[2], se[4]),2),
         lower = round(c(ci.lb[2], b[2]+ci.lb[4]),2),   
         upper = round(c(ci.ub[2], b[2]+ci.ub[4]),2),  
         zval = round(c(zval[2], zval[4]),1),
        pval = round(c(pval[2], pval[4]),3)
       )) 
res_D_dl
```

# Variety 

Yield 

```{r}
dat_bord %>% 
  ggplot()+
  aes(x=variety, y =trial, col =factor(study))+
  geom_point(aes(shape=inc_check_class))+
  scale_shape_manual(values=c(25, 24))+
  theme_bw()+
  coord_flip()+
  theme(axis.text.x=element_text(angle=90, hjust=1, vjust=.5))+
  labs(x="", col="study", shape = "Disease pressure", 
       title = "Disease pressure")
```

```{r}
dat %>%
  distinct(trial, .keep_all = TRUE) %>%
  count(variety) %>% 
  filter(n>3) %>% 
  pull(variety) -> vari

dat_bord %>% 
  filter(variety %in% vari) %>% 
  droplevels()-> dat_bord_vari
```

```{r}
dat_bord_vari %>% 
  ggplot()+
  aes(x=treatment, y =yield, col=inc_check_class)+
  geom_point()+
  geom_line(aes(group=trial))+
  facet_wrap("variety")+
  # scale_shape_manual(values=c(25, 24))+
  theme_bw()

dat_bord_vari %>% 
  group_by(variety, treatment) %>% 
  summarise(y=mean(yield))
```


```{r}
mv_yield_BM_var <- rma.mv(log_yield, log_var_yield,
                     mods = ~treatment*variety,
                     random = list(~treatment | trial),
                     struct = "HCS",
                     method = "ML",
                     data = dat_bord_vari)
```

```{r}
mv_yield_BM_var
anova(mv_yield_BM_var, btt=5:6)
```

```{r net_D_dl, eval=T}
mv_D_BM_var <- rma.mv(yield, var_yield,
                      mods = ~treatment*variety,
                      random = list(~treatment | trial),
                      struct= "UN", 
                      method="ML",
                      data= dat_bord_vari,
                      control = list(optimizer="nlm"))
```

```{r net_D_dl anova}
summary(mv_D_BM_var)
anova(mv_D_BM_var, btt=5:6)

dat_bord_vari %>% 
  count(variety, treatment) %>% 
  bind_cols(
    as_tibble(
      predict(mv_D_BM_var, 
              newmods=rbind(
                c(0,0,0,0,0), # SAGARA LOCAL/AA_CHECK 
                c(1,0,0,0,0), # SAGARA LOCAL/BM1% 
                
                c(0,1,0,0,0), # SHRIWARDHAN/AA_CHECK 
                c(1,1,0,1,0), # SHRIWARDHAN/BM1% 
                
                c(0,0,1,0,0), # SHRIWARDHAN/AA_CHECK 
                c(1,0,1,0,1)  # SHRIWARDHAN/BM1%
              )) 
    )) %>% 
  select(-(cr.lb:tau2.level))

```

So, the treatment-cultivar interaction effect can be interpreted as:
the yield increase due to BM@1% is higher for SAGARA LOCAL and THIRTHAHALLI LOCAL, than for SHRIWARDHAN, which can represent a higher level of tolerance to the disease for the latter variety.

